---
title: "Acceptability"
editor: visual
---

# Acceptability

```{r message=FALSE, echo=FALSE, warning=FALSE}
library(readxl)
library(scorekeeper)
library(tidyverse)

dem_pre_scoresheet <-
read_excel("Demographics/Demographics_preschedule.xlsx")
raw_pre_data <-
read.csv("Demographics/demographics_pre_data.csv")

dem_pre_data <-
scorekeep(raw_pre_data, dem_pre_scoresheet)[[4]] 
```

```{r message=FALSE, echo=FALSE, warning=FALSE}
##demographics postscheduled##

raw_post_data <-
  read_csv("Demographics/Demographics_post_data.csv")

dem_post_scoresheet <-
  read_excel("Demographics/Demographics_postschedule.xlsx")

dem_post_data <-
  scorekeep(raw_post_data, dem_post_scoresheet)[[5]]
```

```{r message=FALSE, echo=FALSE, warning=FALSE}
dem_data <- full_join(dem_pre_data, dem_post_data)
dem_data$dcf_age <- as.Date(dem_data$dcf_age, format = "%m/%d/%y")
dem_data$dcf_date <- as.Date(dem_data$dcf_date, format = "%m/%d/%y")
dem_data$age <- floor(as.numeric(difftime(dem_data$dcf_date, dem_data$dcf_age, units = "days")) / 365.25)
```

```{r message=FALSE, echo=FALSE, warning=FALSE}
###Anovas to compare group dems###

dem_data$dcf_group <- factor(dem_data$dcf_group, levels = c(0, 1), labels = c("Body Project", "BAM"))

sex_anova <- aov(dcf_research_sexual ~ dcf_group, data = dem_data)
summary(sex_anova)

gender_anova <- aov(dcf_research_gender ~ dcf_group, data = dem_data)
summary(gender_anova)

race_anova <- aov(dcf_race ~ dcf_group, data = dem_data)
summary(race_anova)
```

Analyses using a one-way analysis of variance (ANOVA) showed the two groups did not significantly vary based on gender, race, or sexuality. Attrition rate for the BAM intervention was 5% with only 2 participants dropping from the study between the first and second sessions, thus confirming our hypothesis of the BAM intervention attrition being less than 20%. Zero participants dropped out of the Body Project group between intervention sessions. Fifty participants (BAM: N = 26; Body Project: N = 24) completed study activities at all three time points and attended both intervention sessions.

Some participants were also asked to complete a feedback survey about their experience with the BAM intervention at both the post session and 8-week post session time points.
