---
title: "Results"
editor: visual
---

# Results

```{r message=FALSE, echo=FALSE, warning=FALSE}
###Selecting only pps that have completed all 3 timepoints###

completed_participants <- with(BAM_redcap_long_merged, id[ave(timepoint, id, FUN = function(x) length(unique(x))) == 3])

### Split data into BAM and Body Project ###
BAM_dataset <- subset(BAM_redcap_long_merged, id %in% completed_participants & group == 'FP')
Body_Project_dataset <- subset(BAM_redcap_long_merged, id %in% completed_participants & group == 'BP')

###split up the groups by timepoints###
bam_baseline <- subset(BAM_dataset, timepoint == 'baseline')
bam_post <- subset(BAM_dataset, timepoint == 'post')
bam_8week <- subset(BAM_dataset, timepoint == '8wk')

bp_baseline <- subset(Body_Project_dataset, timepoint == 'baseline')
bp_post <- subset(Body_Project_dataset, timepoint == 'post')
bp_8wk <- subset(Body_Project_dataset, timepoint == '8wk')
```

## Fatphobia

## Anti-fat Bias

```{r message=FALSE, echo=FALSE, warning=FALSE}
###BAM UMB-FAT analysis###
mean_fp_umbfat_base <- mean(bam_baseline$umb_total_sum)
mean_fp_umbfat_post <- mean(bam_post$umb_total_sum)
mean_fp_umbfat_wk8 <- mean(bam_8week$umb_total_sum)

sd_fp_umbfat_base <- sd(bam_baseline$umb_total_sum)
sd_fp_umbfat_post <- sd(bam_post$umb_total_sum)
sd_fp_umbfat_wk8 <- sd(bam_8week$umb_total_sum)

cd_fp_umbfat_base_post <- (mean_fp_umbfat_post - mean_fp_umbfat_base) / sqrt((sd_fp_umbfat_base^2 + sd_fp_umbfat_post^2) / 2)
cd_fp_umbfat_base_wk8 <- (mean_fp_umbfat_wk8 - mean_fp_umbfat_base) / sqrt((sd_fp_umbfat_base^2 + sd_fp_umbfat_wk8^2) / 2)
cd_fp_umbfat_post_wk8 <- (mean_fp_umbfat_wk8 - mean_fp_umbfat_post) / sqrt((sd_fp_umbfat_post^2 + sd_fp_umbfat_wk8^2) / 2)

###BP UMB-FAT analysis###
mean_bp_umbfat_base <- mean(bp_baseline$umb_total_sum)
mean_bp_umbfat_post <- mean(bp_post$umb_total_sum)
mean_bp_umbfat_wk8 <- mean(bp_8wk$umb_total_sum)

sd_bp_umbfat_base <- sd(bp_baseline$umb_total_sum)
sd_bp_umbfat_post <- sd(bp_post$umb_total_sum)
sd_bp_umbfat_wk8 <- sd(bp_8wk$umb_total_sum)

cd_bp_umbfat_base_post <- (mean_bp_umbfat_post - mean_bp_umbfat_base) / sqrt((sd_bp_umbfat_base^2 + sd_bp_umbfat_post^2) / 2)
cd_bp_umbfat_base_wk8 <- (mean_bp_umbfat_wk8 - mean_bp_umbfat_base) / sqrt((sd_bp_umbfat_base^2 + sd_bp_umbfat_wk8^2) / 2)
cd_bp_umbfat_post_wk8 <- (mean_bp_umbfat_wk8 - mean_bp_umbfat_post) / sqrt((sd_bp_umbfat_post^2 + sd_bp_umbfat_wk8^2) / 2)
```

```{r message=FALSE, echo=FALSE, warning=FALSE}
###BAM EPSI subscale analysis###

mean_fp_epsi_base <- mean(bam_baseline$epsi_neg_obese_25)
mean_fp_epsi_post <- mean(bam_post$epsi_neg_obese_25)
mean_fp_epsi_wk8 <- mean(bam_8week$epsi_neg_obese_25)

sd_fp_epsi_base <- sd(bam_baseline$epsi_neg_obese_25)
sd_fp_epsi_post <- sd(bam_post$epsi_neg_obese_25)
sd_fp_epsi_wk8 <- sd(bam_8week$epsi_neg_obese_25)

```

Anti-fat Bias was assessed at all three time points for both BAM participants (N = 26) and Body Project participants (N = 24) using the Universal Measure of Bias-FAT (UMB-FAT)[@dursoUnderstandingSelfdirectedStigma2008] and the Eating Pathology Symptoms Inventory (EPSI) negative attitudes toward obesity subcale [@coniglioFactorialIntegrityValidation2018].
