---
title: "Results"
editor: visual
---

# Results

```{r message=FALSE, echo=FALSE, warning=FALSE}
### N for participants at each timepoint###
load("/Volumes/kschaumberg/BAM/EDJTP Pilot Paper/BAM_Paper/Data/BAM_redcap_long_merged.2023_07_14.RData")
fp_base_dataset <- subset(BAM_redcap_long_merged, group == 'FP' & timepoint == 'baseline')
bp_base_dataset <- subset(BAM_redcap_long_merged, group == 'BP' & timepoint == 'baseline')

fp_post_dataset <- subset(BAM_redcap_long_merged, group == 'FP' & timepoint == 'post')
bp_post_dataset <- subset(BAM_redcap_long_merged, group == 'BP' & timepoint == 'post')

fp_8wk_dataset <- subset(BAM_redcap_long_merged, group == 'FP' & timepoint == '8wk')
bp_8wk_dataset <- subset(BAM_redcap_long_merged, group == 'BP' & timepoint == '8wk')

###Selecting only pps that have completed all 3 timepoints###

completed_participants <- with(BAM_redcap_long_merged, id[ave(timepoint, id, FUN = function(x) length(unique(x))) == 3])

### Split data into BAM and Body Project ###
BAM_dataset <- subset(BAM_redcap_long_merged, id %in% completed_participants & group == 'FP')
Body_Project_dataset <- subset(BAM_redcap_long_merged, id %in% completed_participants & group == 'BP')

###split up the groups by timepoints###
bam_baseline <- subset(BAM_dataset, timepoint == 'baseline')
bam_post <- subset(BAM_dataset, timepoint == 'post')
bam_8week <- subset(BAM_dataset, timepoint == '8wk')

bp_baseline <- subset(Body_Project_dataset, timepoint == 'baseline')
bp_post <- subset(Body_Project_dataset, timepoint == 'post')
bp_8wk <- subset(Body_Project_dataset, timepoint == '8wk')
```

## Fatphobia

```{r message=FALSE, echo=FALSE, warning=FALSE}
###BAM GFFS analysis###
mean_fp_gffs_base <- mean(bam_baseline$gffs_sum_25,na.rm = TRUE)
mean_fp_gffs_post <- mean(bam_post$gffs_sum_25,na.rm = TRUE)
mean_fp_gffs_wk8 <- mean(bam_8week$gffs_sum_25,na.rm = TRUE)

sd_fp_gffs_base <- sd(bam_baseline$gffs_sum_25,na.rm = TRUE)
sd_fp_gffs_post <- sd(bam_post$gffs_sum_25,na.rm = TRUE)
sd_fp_gffs_wk8 <- sd(bam_8week$gffs_sum_25,na.rm = TRUE)

cd_fp_gffs_base_post <- (mean_fp_gffs_post - mean_fp_gffs_base) / sqrt((sd_fp_gffs_base^2 + sd_fp_gffs_post^2) / 2)
cd_fp_gffs_base_wk8 <- (mean_fp_gffs_wk8 - mean_fp_gffs_base) / sqrt((sd_fp_gffs_base^2 + sd_fp_gffs_wk8^2) / 2)
cd_fp_gffs_post_wk8 <- (mean_fp_gffs_wk8 - mean_fp_gffs_post) / sqrt((sd_fp_gffs_post^2 + sd_fp_gffs_wk8^2) / 2)

###BP GFFS Analysis###
mean_bp_gffs_base <- mean(bp_baseline$gffs_sum_25,na.rm = TRUE)
mean_bp_gffs_post <- mean(bp_post$gffs_sum_25,na.rm = TRUE)
mean_bp_gffs_wk8 <- mean(bp_8wk$gffs_sum_25,na.rm = TRUE)

sd_bp_gffs_base <- sd(bp_baseline$gffs_sum_25,na.rm = TRUE)
sd_bp_gffs_post <- sd(bp_post$gffs_sum_25,na.rm = TRUE)
sd_bp_gffs_wk8 <- sd(bp_8wk$gffs_sum_25,na.rm = TRUE)

cd_bp_gffs_base_post <- (mean_bp_gffs_post - mean_bp_gffs_base) / sqrt((sd_bp_gffs_base^2 + sd_bp_gffs_post^2) / 2)
cd_bp_gffs_base_wk8 <- (mean_bp_gffs_wk8 - mean_bp_gffs_base) / sqrt((sd_bp_gffs_base^2 + sd_bp_gffs_wk8^2) / 2)
cd_bp_gffs_post_wk8 <- (mean_bp_gffs_wk8 - mean_bp_gffs_post) / sqrt((sd_bp_gffs_post^2 + sd_bp_gffs_wk8^2) / 2)
```

Fatphobia was assessed at the three time points for both BAM (N = 26) and Body Project (N = 24) participants using the Goldfarb Fear of Fat Scale [@goldfarbGoldfarbFearFat1985].

Within the BAM group, the effect sizes for GFFS were as follows:

-   The effect size between baseline and post-session was `r cd_fp_gffs_base_post`, indicating \[interpretation of effect size\].

-   The effect size between baseline and 8 weeks was `r cd_fp_gffs_base_wk8`, indicating \[interpretation of effect size\].

-   The effect size between post-session and 8 weeks was `r cd_fp_gffs_post_wk8`, indicating \[interpretation of effect size\].

Within the Body Project group, the effect sizes for GFFS were as follows:

-   The effect size between baseline and post-session was `r cd_bp_gffs_base_post`, indicating \[interpretation of effect size\].

-   The effect size between baseline and 8 weeks was `r cd_bp_gffs_base_wk8`, indicating \[interpretation of effect size\].

-   The effect size between post-session and 8 weeks was `r cd_bp_gffs_post_wk8`, indicating \[interpretation of effect size\].

## Anti-fat Bias

```{r message=FALSE, echo=FALSE, warning=FALSE}
###BAM UMB-FAT analysis###
mean_fp_umbfat_base <- mean(bam_baseline$umb_total_sum)
mean_fp_umbfat_post <- mean(bam_post$umb_total_sum)
mean_fp_umbfat_wk8 <- mean(bam_8week$umb_total_sum)

sd_fp_umbfat_base <- sd(bam_baseline$umb_total_sum)
sd_fp_umbfat_post <- sd(bam_post$umb_total_sum)
sd_fp_umbfat_wk8 <- sd(bam_8week$umb_total_sum)

cd_fp_umbfat_base_post <- (mean_fp_umbfat_post - mean_fp_umbfat_base) / sqrt((sd_fp_umbfat_base^2 + sd_fp_umbfat_post^2) / 2)
cd_fp_umbfat_base_wk8 <- (mean_fp_umbfat_wk8 - mean_fp_umbfat_base) / sqrt((sd_fp_umbfat_base^2 + sd_fp_umbfat_wk8^2) / 2)
cd_fp_umbfat_post_wk8 <- (mean_fp_umbfat_wk8 - mean_fp_umbfat_post) / sqrt((sd_fp_umbfat_post^2 + sd_fp_umbfat_wk8^2) / 2)

###BP UMB-FAT analysis###
mean_bp_umbfat_base <- mean(bp_baseline$umb_total_sum)
mean_bp_umbfat_post <- mean(bp_post$umb_total_sum)
mean_bp_umbfat_wk8 <- mean(bp_8wk$umb_total_sum)

sd_bp_umbfat_base <- sd(bp_baseline$umb_total_sum)
sd_bp_umbfat_post <- sd(bp_post$umb_total_sum)
sd_bp_umbfat_wk8 <- sd(bp_8wk$umb_total_sum)

cd_bp_umbfat_base_post <- (mean_bp_umbfat_post - mean_bp_umbfat_base) / sqrt((sd_bp_umbfat_base^2 + sd_bp_umbfat_post^2) / 2)
cd_bp_umbfat_base_wk8 <- (mean_bp_umbfat_wk8 - mean_bp_umbfat_base) / sqrt((sd_bp_umbfat_base^2 + sd_bp_umbfat_wk8^2) / 2)
cd_bp_umbfat_post_wk8 <- (mean_bp_umbfat_wk8 - mean_bp_umbfat_post) / sqrt((sd_bp_umbfat_post^2 + sd_bp_umbfat_wk8^2) / 2)
```

```{r message=FALSE, echo=FALSE, warning=FALSE}
###BAM EPSI subscale analysis###
```

Anti-fat Bias was also assessed at all three time points using the Universal Measure of Bias-FAT (UMB-FAT)[@dursoUnderstandingSelfdirectedStigma2008] and the Eating Pathology Symptoms Inventory (EPSI) negative attitudes toward obesity subcale [@coniglioFactorialIntegrityValidation2018].

Within the BAM group, the effect sizes for UMB-FAT were as follows:

-   The effect size between baseline and post-session was `r cd_fp_umbfat_base_post`, indicating \[interpretation of effect size\].

-   The effect size between baseline and 8 weeks was `r cd_fp_umbfat_base_wk8`, indicating \[interpretation of effect size\].

-   The effect size between post-session and 8 weeks was `r cd_fp_umbfat_post_wk8`, indicating \[interpretation of effect size\].

Within the Body Project group, the effect sizes for UMB-FAT were as follows:

-   The effect size between baseline and post-session was `r cd_bp_umbfat_base_post`, indicating \[interpretation of effect size\].

-   The effect size between baseline and 8 weeks was `r cd_bp_umbfat_base_wk8`, indicating \[interpretation of effect size\].

-   The effect size between post-session and 8 weeks was `r cd_bp_umbfat_post_wk8`, indicating \[interpretation of effect size\].

## Thin Ideal Internalization

```{r message=FALSE, echo=FALSE, warning=FALSE}
###BAM SATAQ Analysis###
mean_fp_sataq_base <- mean(bam_baseline$sataq_average)
mean_fp_sataq_post <- mean(bam_post$sataq_average)
mean_fp_sataq_wk8 <- mean(bam_8week$sataq_average)

sd_fp_sataq_base <- sd(bam_baseline$sataq_average)
sd_fp_sataq_post <- sd(bam_post$sataq_average)
sd_fp_sataq_wk8 <- sd(bam_8week$sataq_average)

cd_fp_sataq_base_post <- (mean_fp_sataq_post - mean_fp_sataq_base) / sqrt((sd_fp_sataq_base^2 + sd_fp_sataq_post^2) / 2)
cd_fp_sataq_base_wk8 <- (mean_fp_sataq_wk8 - mean_fp_sataq_base) / sqrt((sd_fp_sataq_base^2 + sd_fp_sataq_wk8^2) / 2)
cd_fp_sataq_post_wk8 <- (mean_fp_sataq_wk8 - mean_fp_sataq_post) / sqrt((sd_fp_sataq_post^2 + sd_fp_sataq_wk8^2) / 2)

###BP SATAQ Analysis###
mean_bp_sataq_base <- mean(bp_baseline$sataq_average)
mean_bp_sataq_post <- mean(bp_post$sataq_average)
mean_bp_sataq_wk8 <- mean(bp_8wk$sataq_average, na.rm = TRUE)

sd_bp_sataq_base <- sd(bp_baseline$sataq_average)
sd_bp_sataq_post <- sd(bp_post$sataq_average)
sd_bp_sataq_wk8 <- sd(bp_8wk$sataq_average, na.rm = TRUE)

cd_bp_sataq_base_post <- (mean_bp_sataq_post - mean_bp_sataq_base) / sqrt((sd_bp_sataq_base^2 + sd_bp_sataq_post^2) / 2)
cd_bp_sataq_base_wk8 <- (mean_bp_sataq_wk8 - mean_bp_sataq_base) / sqrt((sd_bp_sataq_base^2 + sd_bp_sataq_wk8^2) / 2)
cd_bp_sataq_post_wk8 <- (mean_bp_sataq_wk8 - mean_bp_sataq_post) / sqrt((sd_bp_sataq_post^2 + sd_bp_sataq_wk8^2) / 2)
```

```{r message=FALSE, echo=FALSE, warning=FALSE}
###BAM IBSS-R Analysis###
mean_fp_ibssr_base <- mean(bam_baseline$ibssr_mean_25, na.rm = TRUE)
mean_fp_ibssr_post <- mean(bam_post$ibssr_mean_25, na.rm = TRUE)
mean_fp_ibssr_wk8 <- mean(bam_8week$ibssr_mean_25, na.rm = TRUE)

sd_fp_ibssr_base <- sd(bam_baseline$ibssr_mean_25, na.rm = TRUE)
sd_fp_ibssr_post <- sd(bam_post$ibssr_mean_25, na.rm = TRUE)
sd_fp_ibssr_wk8 <- sd(bam_8week$ibssr_mean_25, na.rm = TRUE)

cd_fp_ibssr_base_post <- (mean_fp_ibssr_post - mean_fp_ibssr_base) / sqrt((sd_fp_ibssr_base^2 + sd_fp_ibssr_post^2) / 2)
cd_fp_ibssr_base_wk8 <- (mean_fp_ibssr_wk8 - mean_fp_ibssr_base) / sqrt((sd_fp_ibssr_base^2 + sd_fp_ibssr_wk8^2) / 2)
cd_fp_ibssr_post_wk8 <- (mean_fp_ibssr_wk8 - mean_fp_ibssr_post) / sqrt((sd_fp_ibssr_post^2 + sd_fp_ibssr_wk8^2) / 2)

###BP IBSSR Analysis###
mean_bp_ibssr_base <- mean(bp_baseline$ibssr_mean_25, na.rm = TRUE)
mean_bp_ibssr_post <- mean(bp_post$ibssr_mean_25, na.rm = TRUE)
mean_bp_ibssr_wk8 <- mean(bp_8wk$ibssr_mean_25, na.rm = TRUE)

sd_bp_ibssr_base <- sd(bp_baseline$ibssr_mean_25, na.rm = TRUE)
sd_bp_ibssr_post <- sd(bp_post$ibssr_mean_25, na.rm = TRUE)
sd_bp_ibssr_wk8 <- sd(bp_8wk$ibssr_mean_25, na.rm = TRUE)

cd_bp_ibssr_base_post <- (mean_bp_ibssr_post - mean_bp_ibssr_base) / sqrt((sd_bp_ibssr_base^2 + sd_bp_ibssr_post^2) / 2)
cd_bp_ibssr_base_wk8 <- (mean_bp_ibssr_wk8 - mean_bp_ibssr_base) / sqrt((sd_bp_ibssr_base^2 + sd_bp_ibssr_wk8^2) / 2)
cd_bp_ibssr_post_wk8 <- (mean_bp_ibssr_wk8 - mean_bp_ibssr_post) / sqrt((sd_bp_ibssr_post^2 + sd_bp_ibssr_wk8^2) / 2)
```

Furthermore, thin ideal internalization was assessed using the Sociocultural Attitudes Towards Appearance Questionnaire (SATAQ) [@schaeferDevelopmentValidationSociocultural2015] and the Ideal Body Stereotype Scale - Revised (IBSS-R) [@sticeTestDualPathway1996].

Within the BAM group, the effect sizes for SATAQ were as follows:

-   The effect size between baseline and post-session was `r cd_fp_sataq_base_post`, indicating \[interpretation of effect size\].

-   The effect size between baseline and 8 weeks was `r cd_fp_sataq_base_wk8`, indicating \[interpretation of effect size\].

-   The effect size between post-session and 8 weeks was `r cd_fp_sataq_post_wk8`, indicating \[interpretation of effect size\].

Within the Body Project group, the effect sizes for SATAQ were as follows:

-   The effect size between baseline and post-session was `r cd_bp_sataq_base_post`, indicating \[interpretation of effect size\].

-   The effect size between baseline and 8 weeks was `r cd_bp_sataq_base_wk8`, indicating \[interpretation of effect size\].

-   The effect size between post-session and 8 weeks was `r cd_bp_sataq_post_wk8`, indicating \[interpretation of effect size\].

Furthermore, the effect sizes for the IBSS-R for the BAM group were:

-   The effect size between baseline and post-session was `r cd_fp_ibssr_base_post`, indicating \[interpretation of effect size\].

-   The effect size between baseline and 8 weeks was `r cd_fp_ibssr_base_wk8`, indicating \[interpretation of effect size\].

-   The effect size between post-session and 8 weeks was `r cd_fp_ibssr_post_wk8`, indicating \[interpretation of effect size\].

Within the Body Project group, the effect sizes for IBSS-R were as follows:

-   The effect size between baseline and post-session was `r cd_bp_ibssr_base_post`, indicating \[interpretation of effect size\].

-   The effect size between baseline and 8 weeks was `r cd_bp_ibssr_base_wk8`, indicating \[interpretation of effect size\].

-   The effect size between post-session and 8 weeks was `r cd_bp_ibssr_post_wk8`, indicating \[interpretation of effect size\].
