---
title: "Sample Description"
format: html
editor: visual
---

# Sample Description

```{r message=FALSE, echo=FALSE, warning=FALSE}
library(readxl)
library(scorekeeper)
library(tidyverse)

setwd("/Volumes/kschaumberg/BAM/EDJTP Pilot Paper/BAM_Paper/Demographics")

dem_pre_scoresheet <-
read_excel("/Volumes/kschaumberg/BAM/EDJTP Pilot Paper/BAM_Paper/Demographics/Demographics_preschedule.xlsx")
dem_pre_data_unscored <-
read.csv("/Volumes/kschaumberg/BAM/EDJTP Pilot Paper/BAM_Paper/Demographics/demographics_pre_data.csv")

dem_pre_data <-
scorekeep(dem_pre_data_unscored, dem_pre_scoresheet)[[3]]
```

```{r message=FALSE, echo=FALSE, warning=FALSE}
##demographics postscheduled##

raw_post_data <-
  read_csv("/Volumes/kschaumberg/BAM/EDJTP Pilot Paper/BAM_Paper/Demographics/Demographics_post_data.csv")

demographic_scoresheet <-
  read_excel("/Volumes/kschaumberg/BAM/EDJTP Pilot Paper/BAM_Paper/Demographics/Demographics_postschedule.xlsx")

dem_post_data <-
  scorekeep(raw_post_data, demographic_scoresheet)[[5]]

```

```{r message=FALSE, echo=FALSE, warning=FALSE}
dem_data <- full_join(dem_pre_data, dem_post_data)
dem_data <- dem_data[-31, ]
dem_data$dcf_age <- as.Date(dem_data$dcf_age, format = "%m/%d/%y")
dem_data$dcf_date <- as.Date(dem_data$dcf_date, format = "%m/%d/%y")
dem_data$age <- floor(as.numeric(difftime(dem_data$dcf_date, dem_data$dcf_age, units = "days")) / 365.25)
```

```{r message=FALSE, echo=FALSE, warning=FALSE}
age_excluded <- dem_data$age[-15]
mean_age <- mean(age_excluded, na.rm = TRUE)
excluded_data <- dem_data[-15, ]
oldest_age <- max(excluded_data$age, na.rm = TRUE)
youngest_age <- min(excluded_data$age, na.rm = TRUE)


percent_white <- round((mean(dem_data$dcf_race == 1, na.rm = TRUE) * 100), 2)
percent_black <- round((mean(dem_data$dcf_race == 2, na.rm = TRUE) * 100), 2)
percent_asian <- round((mean(dem_data$dcf_race == 3, na.rm = TRUE) * 100), 2)
percent_native <- round((mean(dem_data$dcf_race == 4, na.rm = TRUE) * 100), 2)
percent_hispanic <- round((mean(dem_data$dcf_race == 5, na.rm = TRUE) * 100), 2)
percent_pacific <- round((mean(dem_data$dcf_race == 6, na.rm = TRUE) * 100), 2)

percent_women <- round((mean(dem_data$dcf_research_gender == 2, na.rm = TRUE) * 100), 2)

percent_heterosexual <- round((mean(dem_data$dcf_research_sexual == 1, na.rm = TRUE) * 100), 2)
percent_homosexual <- round((mean(dem_data$dcf_research_sexual == 2, na.rm = TRUE) * 100), 2)
percent_bisexual <- round((mean(dem_data$dcf_research_sexual == 3, na.rm = TRUE) * 100), 2)

percent_student <- round((mean(dem_data$dcf_student == 1, na.rm = TRUE) * 100), 2)
sum_student <- sum(dem_data$dcf_student, na.rm = TRUE)
```


66 participants were randomly assigned to either the BAM (N=38) or the Body Project (N=28) intervention. Of these, XX attended the interventions virtually (BAM: N=XX, BP: N=XX) beginning 09/20 and ending 02/22 due to the pandemic. Participants ranged in age from `r youngest_age` -- `r oldest_age` with the average age being `r mean_age`. Participants were mostly women (`r percent_women`). Participants were also mostly White (`r percent_white`) followed by Asian (`r percent_asian`) then Black (`r percent_black`). Furthermore, the majority of participants identified as heterosexual (`r percent_heterosexual`) (bisexual: `r percent_bisexual`; homosexual: `r percent_homosexual`). At the time of the intervention, `r sum_student` participants reported being students. 56 participants that attended sessions completed the initial post-session study activities and the the 8-week post-session activities.